---
title: 'Reduplication study: GCA analysis and model comparisons - New Coding'
author: "Aitor San Jose, Mits Ota, Kenny Smith"
date: "13 September 2019"
output:
  html_notebook:
    number_sections: yes
    toc: yes
  html_document:
    df_print: paged
    toc: yes
---


# Preamble
These are GCA analyses and model comparisons run for the reduplication study. Originally in raw R script, now in R Notebook format. It saves tables as .doc files and plots as .pdf files. *This one uses the new coding of phonological repeition implemented by Kenny*.


# Packages
```{r}
library(ggplot2)
library(broom)
library(lme4)
library(bbmle)
library(lmerTest)
library(sjPlot)
```

# Data preparation
## Data read-in
This reads in the new dataset that includes the new coding of syllable and consonant repetition. But the script replaces the old equivalents (Adj_B, New_Redup_B) with the new variables (SyllableRepetition, ConsonantRepetition). 
```{r}
df = read.table(file="data_june_2018_recoded2.csv", na.strings=c("", "NA"), sep=",", header=TRUE)
df = subset(df, select = -c(New_Redup_B, Adj_B)) 
colnames(df)[c(46, 47)] <- c("Adj_B", "New_Redup_B") 
colnames(df)[6] <- "Unique_language"
df$Trial_Iteration[is.na(df$Trial_Iteration)] <- 0 #make NAs 0 for next line to work
df <-subset(df,Trial_Iteration != 1)  # keep seed languages and second round of iterations
# df <- subset(df, Transmitter == 1) # uncomment to keep only the data from the participants whose language was used to train the following generation

df_director<-subset(df,Stage!='interactM') # includes seed languages
df_matcher<-subset(df,Stage=='interactM') # includes only generations 1 to 5, since there is no accuracy for seed languages
df_director_generations_1_to_5 <- subset(df_director, Generation > 0) #excludes seed languages
```

## Sum-coding
```{r}
contrasts(df_director$LexiconType) = contr.sum(2)
contrasts(df_director$GroupType) = contr.sum(2)
contrasts(df_matcher$LexiconType) = contr.sum(2)
contrasts(df_matcher$GroupType) = contr.sum(2)
```

## Adding 3rd-order polynomials for GCA

```{r}
df_director$timebin = df_director$Generation + 1
t = poly(unique(df_director$timebin), 3)
df_director[,paste("ot", 1:3, sep="")] <- t[df_director$timebin, 1:3]

df_matcher$timebin = df_matcher$Generation
t = poly(unique(df_matcher$timebin), 3)
df_matcher[,paste("ot", 1:3, sep="")] <- t[df_matcher$timebin, 1:3]
```


# Analysis of consonant repetition ("CVC")

## CVC: Full models
```{r}
# CVC_third_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to cubic term 
#                 (ot1+ot2+ot3) * GroupType * LexiconType + (1+ot1+ot2+ot3|Unique_Participant) + 
#                 (1+ot1+ot2+ot3 |Meaning) + (1+ot1+ot2+ot3|Pair), data=df_director, family=binomial, 
#                 control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

#CVC_second_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to quadratic term 
#                 (ot1+ot2) * GroupType * LexiconType + (1+ot1+ot2|Unique_Participant) + 
#                 (1+ot1+ot2 |Meaning) + (1+ot1+ot2|Pair), data=df_director, family=binomial, 
#                 control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

#CVC_first_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to linear term 
#                 ot1 * GroupType * LexiconType + (1+ot1|Unique_Participant) + (1+ot1 |Meaning) + 
#                 (1+ot1+ot2|Pair), data=df_director, family=binomial, 
#                 control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))    
```

## CVC: Reduced models              
The full models above all result in singular fit. The models converge without singular fit when all the random slopes are removed and 'Pair' is also removed as a random effect.Below are models with these terms dropped.
```{r}
CVC_third_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to cubic term 
                  (ot1+ot2+ot3) * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                  data=df_director, family=binomial, 
                  control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

CVC_second_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to quadratic term 
                    (ot1+ot2) * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                   data=df_director, family=binomial, 
                   control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

CVC_first_order <- glmer(New_Redup_B ~ #maximal random effect structure, up to linear term                          
                    ot1 * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                    data=df_director, family=binomial, 
                    control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
summary(CVC_third_order)
summary(CVC_second_order)
summary(CVC_first_order)
```

## CVC: Model comparison
```{r}
CVC_model.names <- c("CVC first order","CVC second order","CVC third order")
CVC_summ.table <- do.call(rbind, lapply(list(CVC_first_order,CVC_second_order,CVC_third_order), broom::glance))
CVC_table.cols <- c("df.residual", "deviance", "AIC")
CVC_reported.table <- CVC_summ.table[CVC_table.cols]
names(CVC_reported.table) <- c("Resid.Df", "Resid.Dev", "AIC")
CVC_reported.table[['dAIC']] <-  with(CVC_reported.table, AIC - min(AIC))
CVC_reported.table[['AIC_weight']] <- with(CVC_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
CVC_reported.table$AIC <- NULL
CVC_reported.table$AIC_weight <- round(CVC_reported.table$AIC_weight, 2)
CVC_reported.table$dAIC <- round(CVC_reported.table$dAIC, 1)
CVC_reported.table$Resid.Dev <- round(CVC_reported.table$Resid.Dev, 2)
row.names(CVC_reported.table) <- CVC_model.names
View(CVC_reported.table)
sjPlot::tab_df(CVC_reported.table,
       file="model comparison CVC.doc")
```

## CVC: Plots showing model fit of 1st and 2nd order models by group type
```{r}
ggplot(df_director, aes(Generation, New_Redup_B, shape=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(CVC_first_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Consonant repetition")+ 
  ggtitle('Consonant repetition by group type - first order model')
dev.print(pdf, 'Consonant repetition by group type - first order model.pdf')

ggplot(df_director, aes(Generation, New_Redup_B, color=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(CVC_second_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("CVC repetition")+ 
  ggtitle('CVC repetition by group type - second order model')
dev.print(pdf,'CVC repetition by group type - second order model.pdf')

# sjPlot::tab_df(round(coef(summary(CVC_first_order)),3),file='CVC_fixed_effects.doc')
# sjPlot::tab_df(as.numeric(VarCorr(CVC_first_order)),file='CVC_random_effects.doc')
```

## CVC: Plots showing model fit of 1st and 2nd order models by lexicon type
```{r}
ggplot(df_director, aes(Generation, New_Redup_B, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(CVC_first_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("CVC repetition") + 
  ggtitle('CVC repetition by lexicon type - first order model')
dev.print(pdf,'CVC repetition by lexicon type - first order model.pdf')


ggplot(df_director, aes(Generation, New_Redup_B, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(CVC_second_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("CVC repetition") + 
  ggtitle('CVC repetition by lexicon type - second order model')
dev.print(pdf,'CVC repetition by lexicon type - second order model.pdf')
```

# Analysis of adjacent syllable repetition

## Syllable repetition: Full models
```{r}
# ADJ_third_order <- glmer(Adj_B ~ #maximal random effect structure, up to cubic term 
#                   (ot1+ot2+ot3) * GroupType * LexiconType + (1+ot1+ot2+ot3|Unique_Participant) + 
#                   (1+ot1+ot2+ot3 |Meaning) + (1+ot1+ot2+ot3|Pair), data=df_director, family=binomial, 
#                   control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


# ADJ_second_order <- glmer(Adj_B ~ #maximal random effect structure, up to quadratic term 
#                   (ot1+ot2) * GroupType * LexiconType + (1+ot1+ot2|Unique_Participant) + 
#                   (1+ot1+ot2 |Meaning) + (1+ot1+ot2|Pair),
#                   data=df_director, family=binomial, 
#                   control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


# ADJ_first_order <- glmer(Adj_B ~ #maximal random effect structure, up to linear term 
#                   ot1 * GroupType * LexiconType + (1+ot1|Unique_Participant) + 
#                   (1+ot1 |Meaning) + (1+ot1|Pair), data=df_director, family=binomial, 
#                   control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
```

## Syllable repetition: Reduced models
The full models above also result in singular fit. So they are reduced below.
```{r}
ADJ_third_order <- glmer(Adj_B ~ #maximal random effect structure, up to cubic term 
                         (ot1+ot2+ot3) * GroupType * LexiconType + (1|Unique_Participant) + 
                           (1|Meaning), data=df_director, family=binomial, 
                         control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


ADJ_second_order <- glmer(Adj_B ~ #maximal random effect structure, up to quadratic term 
                      (ot1+ot2) * GroupType * LexiconType + (1|Unique_Participant) + 
                        (1|Meaning), data=df_director, family=binomial, 
                      control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


ADJ_first_order <- glmer(Adj_B ~ #maximal random effect structure, up to linear term 
                        ot1 * GroupType * LexiconType + (1|Unique_Participant) + 
                          (1|Meaning), data=df_director, family=binomial, 
                        control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
summary(ADJ_third_order)
summary(ADJ_second_order)
summary(ADJ_first_order)
```


## Syllable repetition: Model comparison
```{r}
ADJ_model.names <- c("ADJ first order","ADJ second order","ADJ third order")
ADJ_summ.table <- do.call(rbind, lapply(list(ADJ_first_order,ADJ_second_order,ADJ_third_order), broom::glance))
ADJ_table.cols <- c("df.residual", "deviance", "AIC")
ADJ_reported.table <- ADJ_summ.table[ADJ_table.cols]
names(ADJ_reported.table) <- c("Resid.Df", "Resid.Dev", "AIC")
ADJ_reported.table[['dAIC']] <-  with(ADJ_reported.table, AIC - min(AIC))
ADJ_reported.table[['AIC_weight']] <- with(ADJ_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
ADJ_reported.table$AIC <- NULL
ADJ_reported.table$AIC_weight <- round(ADJ_reported.table$AIC_weight, 2)
ADJ_reported.table$dAIC <- round(ADJ_reported.table$dAIC, 1)
ADJ_reported.table$Resid.Dev <- round(ADJ_reported.table$Resid.Dev, 2)

row.names(ADJ_reported.table) <- ADJ_model.names
View(ADJ_reported.table)

sjPlot::tab_df(ADJ_reported.table,
               file="model comparison _ADJ.doc")

sjPlot::tab_df(round(coef(summary(ADJ_first_order)),3),file='ADJ_fixed_effects.doc')
```


## Syllable repetition: Plots showing model fit of 1st and 2nd order models by group type
```{r}
df_director_adj_plots <- subset(df_director, !(is.na(df_director$Adj_B)))

  
ggplot(df_director_adj_plots, aes(Generation, Adj_B, shape=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ADJ_first_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Adjacent repetition")+ 
  ggtitle('Adjacent repetition by group type - first order model')
dev.print(pdf,'Adjacent repetition by group type - first order model.pdf')

ggplot(df_director_adj_plots, aes(Generation, Adj_B, color=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ADJ_second_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Adjacent Repetition") +
  ggtitle('Adjacent repetition by group type - second order model')
dev.print(pdf,'Adjacent repetition by group type - second order model.pdf')
```

## Syllable repetition: Plots showing model fit of 1st and 2nd order models by lexicon type
```{r}
ggplot(df_director_adj_plots, aes(Generation, Adj_B, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ADJ_first_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Adjacent repetition")+ 
  ggtitle('Adjacent repetition by lexicon type - first order model')
dev.print(pdf,'Adjacent repetition by lexicon type - first order model.pdf')


ggplot(df_director_adj_plots, aes(Generation, Adj_B, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ADJ_second_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Adjacent repetition")+ 
  ggtitle('Adjacent repetition by lexicon type - second order model')
dev.print(pdf,'Adjacent repetition by lexicon type - second order model.pdf')
```

# Accuracy

## Accuracy: Full models
```{r}
#ACC_first_order <- glmer(Score ~ #maximal random effect structure, up to linear term 
#                        ot1 * GroupType * LexiconType  + (1+ot1|Unique_Participant) + 
#                       (1+ot1 |Meaning) + (1+ot1|Pair), data=df_matcher, family=binomial, 
#                       control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


#ACC_second_order <- glmer(Score ~ #maximal random effect structure, up to quadratic term 
#                     (ot1+ot2) * GroupType * LexiconType + (1+ot1+ot2|Unique_Participant) + 
#                     (1+ot1+ot2 |Meaning) + (1+ot1+ot2|Pair), data=df_matcher, family=binomial, 
#                     control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

#ACC_third_order <- glmer(Score ~ #maximal random effect structure, up to cubic term 
#                     (ot1+ot2+ot3) * GroupType * LexiconType + (1+ot1+ot2+ot3|Unique_Participant) + 
#                   (1+ot1+ot2+ot3 |Meaning) + (1+ot1+ot2+ot3|Pair), data=df_matcher, family=binomial, 
#                   control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
```

## Accuracy: Reduced models
The full models above also result in singular fit. So they are reduced below.
```{r}
ACC_first_order <- glmer(Score ~ #maximal random effect structure, up to linear term 
                         ot1 * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                       data=df_matcher, family=binomial, 
                       control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

ACC_second_order <- glmer(Score ~ #maximal random effect structure, up to quadratic term 
                      (ot1+ot2) * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                    data=df_matcher, family=binomial, 
                    control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

ACC_third_order <- glmer(Score ~ #maximal random effect structure, up to cubic term 
                      (ot1+ot2+ot3) * GroupType * LexiconType + (1|Unique_Participant) + (1|Meaning),
                    data=df_matcher, family=binomial, 
                    control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
summary(ACC_third_order)
summary(ACC_second_order)
summary(ACC_first_order)
```


## Accuracy: Model comparison
```{r}
ACC_model.names <- c("ACC first order","ACC second order","ACC third order")
ACC_summ.table <- do.call(rbind, lapply(list(ACC_first_order,ACC_second_order,ACC_third_order), broom::glance))
ACC_table.cols <- c("df.residual", "deviance", "AIC")
ACC_reported.table <- ACC_summ.table[ACC_table.cols]
names(ACC_reported.table) <- c("Resid.Df", "Resid.Dev", "AIC")
ACC_reported.table[['dAIC']] <-  with(ACC_reported.table, AIC - min(AIC))
ACC_reported.table[['AIC_weight']] <- with(ACC_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
ACC_reported.table$AIC <- NULL
ACC_reported.table$dAIC <- round(ACC_reported.table$dAIC, 1)
ACC_reported.table$AIC_weight <- round(ACC_reported.table$AIC_weight, 2)
ACC_reported.table$Resid.Dev <- round(ACC_reported.table$Resid.Dev, 2)
row.names(ACC_reported.table) <- ACC_model.names
View(ACC_reported.table)
sjPlot::tab_df(ACC_reported.table,
               file="model comparison _ACC.doc")
```


## Accuracy: Plots showing model fit of 1st and 2nd order models by group type
```{r}
ggplot(df_matcher, aes(Generation, Score, shape=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ACC_first_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Accuracy")+ 
  ggtitle('Accuracy by group type - first order model')
dev.print(pdf,'Accuracy by group type - first order model.pdf')

ggplot(df_matcher, aes(Generation, Score, color=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ACC_second_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Accuracy")+ 
  ggtitle('Accuracy by group type - second order model')
dev.print(pdf,'Accuracy by group type - second order model.pdf')

```


## Accuracy: Plots showing model fit of 1st and 2nd order models by lexicon type
```{r}
ggplot(df_matcher, aes(Generation, Score, shape=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ACC_first_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Accuracy")+ 
  ggtitle('Accuracy by lexicon type - first order model')
dev.print(pdf,'Accuracy by lexicon type - first order model.pdf')

ggplot(df_matcher, aes(Generation, Score, shape=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(ACC_second_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Accuracy")+ 
  ggtitle('Accuracy by lexicon type - second order model')
dev.print(pdf,'Accuracy by lexicon type - second order model.pdf')

sjPlot::tab_df(round(coef(summary(ACC_first_order)),3),file='ACC_fixed_effects.doc')
```

# Homonymy

## Coding homonymy
These are based on iteration 2 only. Homonymy is calculated as proportions.
```{r}
df_homonymy<-setNames(aggregate(df_director_generations_1_to_5$New_Redup_B, by=list(df_director_generations_1_to_5$GroupType,df_director_generations_1_to_5$LexiconType,df_director_generations_1_to_5$GroupNumber,df_director_generations_1_to_5$Generation,df_director_generations_1_to_5$Unique_language,df_director_generations_1_to_5$Pair, df_director_generations_1_to_5$Unique_Participant), FUN=mean),c('GroupType','LexiconType','GroupNumber','Generation','Unique_language','Pair', 'Unique_Participant','New_Redup_B_mean'))
df_homonymy$Word_repetition<-NA

for(i in unique(df_homonymy$Unique_language)){
  subs_ <- subset(df_director_generations_1_to_5,Unique_language==i)
  for(j in 1:nrow(df_homonymy)){
    if(toString(df_homonymy[j,]$Unique_language) == i){
      df_homonymy[j,]$Word_repetition <- (length(subs_$TypedLabel)-length(unique(subs_$TypedLabel)))/length(subs_$TypedLabel)
      
    }
  }
}

initial_languages<-subset(df_director,Generation==0)
df_initial_languages <-setNames(aggregate(initial_languages$New_Redup_B, by=list(initial_languages$GroupType,initial_languages$LexiconType,initial_languages$GroupNumber,initial_languages$Generation,initial_languages$Unique_language,initial_languages$Pair, initial_languages$Unique_Participant), FUN=mean),c('GroupType','LexiconType','GroupNumber','Generation','Unique_language','Pair', 'Unique_Participant','New_Redup_B_mean'))
df_initial_languages$Word_repetition <-0
df_homonymy<-rbind(df_initial_languages,df_homonymy)

df_homonymy_1_to_5 <- subset(df_homonymy, Generation>0) #generations 1 to 5
cor(df_homonymy_1_to_5$New_Redup_B_mean,df_homonymy_1_to_5$Word_repetition) #looking at mean CVC redup. When looking at sum CVC redup the correlation was .20...

df_homonymy$timebin = df_homonymy$Generation + 1
t_ = poly(unique(df_homonymy$timebin), 3)
df_homonymy[,paste("ot", 1:3, sep="")] <- t_[df_homonymy$timebin, 1:3]

contrasts(df_homonymy$LexiconType) = contr.sum(2)
contrasts(df_homonymy$GroupType) = contr.sum(2)
```

## Homonymy: Models
Can't fit a 3rd order model because there are fewer observations than random effects
```{r}
homonymy_first_order <- lmer(Word_repetition ~
                          ot1*GroupType*LexiconType +
                          (1|Unique_Participant),
                        data=df_homonymy, control=lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))


homonymy_second_order <- lmer(Word_repetition ~
                          (ot1+ot2)*GroupType*LexiconType +
                            (1|Unique_Participant),
                        data=df_homonymy, control=lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=2e5)))
summary(homonymy_first_order)
summary(homonymy_second_order)
```

## Homonymy: Model comparison
```{r}
homonyms_model.names <- c("Homonymy first order","Homonymy second order")
homonyms_summ.table <- do.call(rbind, lapply(list(homonymy_first_order,homonymy_second_order), broom::glance))
homonyms_table.cols <- c("df.residual", "deviance", "AIC")
homonyms_reported.table <- homonyms_summ.table[homonyms_table.cols]
names(homonyms_reported.table) <- c("Resid. Df", "Resid.Dev", "AIC")
homonyms_reported.table[['dAIC']] <-  with(homonyms_reported.table, AIC - min(AIC))
homonyms_reported.table[['AIC_weight']] <- with(homonyms_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
homonyms_reported.table$AIC <- NULL
homonyms_reported.table$AIC_weight <- round(homonyms_reported.table$AIC_weight, 2)
homonyms_reported.table$dAIC <- round(homonyms_reported.table$dAIC, 1)
homonyms_reported.table$Resid.Dev <- round(homonyms_reported.table$Resid.Dev, 2)
row.names(homonyms_reported.table) <- homonyms_model.names
View(homonyms_reported.table)
anova(homonymy_first_order,homonymy_second_order)
sjPlot::tab_df(homonyms_reported.table,
               file="model comparison homonyms_.doc")

sjPlot::tab_df(round(coef(summary(homonymy_first_order)),3),file='homonyms_fixed_effects.doc')
```


## Homonymy: Plots showing model fit of 1st and 2nd order models by group type
```{r}
ggplot(df_homonymy, aes(Generation, Word_repetition, shape=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_first_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy by group type - first order model.pdf')

ggplot(df_homonymy, aes(Generation, Word_repetition, color=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_second_order), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy by group type - second order model.pdf')
```


## Homonymy: Plots showing model fit of 1st and 2nd order models by lexicon type
```{r}
ggplot(df_homonymy, aes(Generation, Word_repetition, shape=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_first_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy")
dev.print(pdf,'Homonymy by lexicon type - first order model.pdf')

ggplot(df_homonymy, aes(Generation, Word_repetition, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_second_order), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy by lexicon type - second order model.pdf')
```

# Homonymy: Logistic analysis

Analyze homonymy again, using 0/1 coding for word repetition and binomial stats

## Homonymy (log): Models
```{r}
df_homonymy$Word_repetition_binary = ifelse(df_homonymy$Word_repetition > 0, 1, 0)

homonymy_first_order_log <- glmer(Word_repetition_binary ~
                               ot1*GroupType*LexiconType + (1|Unique_Participant),
                             data=df_homonymy, family=binomial, 
                             control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

homonymy_second_order_log <- glmer(Word_repetition_binary ~
                                    (ot1+ot2)*GroupType*LexiconType + (1|Unique_Participant),
                                  data=df_homonymy, family=binomial, 
                                  control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


homonymy_third_order_log <- glmer(Word_repetition_binary ~
                                     (ot1+ot2+ot3)*GroupType*LexiconType + (1|Unique_Participant),
                                   data=df_homonymy, family=binomial, 
                                  control=glmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))

summary(homonymy_first_order_log)
summary(homonymy_second_order_log)
summary(homonymy_third_order_log)
```
```{r}
numcols <- grep("^c\\.",names(df_homonymy))
dfs_homonymy <- df_homonymy
dfs_homonymy[,numcols] <- scale(dfs_homonymy[,numcols])
homonymy_first_order_log_sc <- update(homonymy_first_order_log, data=dfs_homonymy)
homonymy_second_order_log_sc <- update(homonymy_second_order_log, data=dfs_homonymy)

```


## Homonymy (log): Model comparison
Model comparison shows that the second-order model has the best fit.
```{r}
homonyms_log_model.names <- c("Homonymy first order log","Homonymy second order log", "Homonymy third order log")
homonyms_log_summ.table <- do.call(rbind, lapply(list(homonymy_first_order_log,homonymy_second_order, homonymy_third_order_log), broom::glance))
homonyms_log_table.cols <- c("df.residual", "deviance", "AIC")
homonyms_log_reported.table <- homonyms_log_summ.table[homonyms_log_table.cols]
names(homonyms_log_reported.table) <- c("Resid. Df", "Resid.Dev", "AIC")
homonyms_log_reported.table[['dAIC']] <-  with(homonyms_log_reported.table, AIC - min(AIC))
homonyms_log_reported.table[['AIC_weight']] <- with(homonyms_log_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
homonyms_log_reported.table$AIC <- NULL
homonyms_log_reported.table$AIC_weight <- round(homonyms_log_reported.table$AIC_weight, 2)
homonyms_log_reported.table$dAIC <- round(homonyms_log_reported.table$dAIC, 1)
homonyms_log_reported.table$Resid.Dev <- round(homonyms_log_reported.table$Resid.Dev, 2)
row.names(homonyms_log_reported.table) <- homonyms_log_model.names
View(homonyms_log_reported.table)
anova(homonymy_first_order_log,homonymy_second_order_log, homonymy_third_order_log)
sjPlot::tab_df(homonyms_log_reported.table,
               file="model comparison homonyms log_.doc")

sjPlot::tab_df(round(coef(summary(homonymy_first_order_log)),3),file='homonyms_log_fixed_effects.doc')
homonyms_log_reported.table

```

## Homonymy (log): Plot showing model fit of 2nd order models by group type x lexicon size

```{r}
ggplot(df_homonymy, aes(Generation, Word_repetition_binary, shape=GroupType, linetype=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_second_order_log), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy")
dev.print(pdf,'Homonymy Log by Group and Lexicon type - first order model.pdf')
```

# Homonymy (Gen1-5)
Because there's discontinuity between Generation/Round 0 and 1, redo the analysis in 'Homonymy' without Generation/Round 0 (i.e., only Generations 1-5).

## Homonymy (Gen1-5): Models
Can't fit a 3rd order model because there are fewer observations than random effects
```{r}

homonymy_first_order_1to5 <- lmer(Word_repetition ~
                               ot1*GroupType*LexiconType + (1|Unique_Participant),
                             data=df_homonymy[df_homonymy$Generation != 0, ], 
                             control=lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))


homonymy_second_order_1to5 <- lmer(Word_repetition ~
                                (ot1+ot2)*GroupType*LexiconType + (1|Unique_Participant),
                              data=df_homonymy[df_homonymy$Generation != 0, ], 
                              control=lmerControl(optimizer = "bobyqa", optCtrl=list(maxfun=1e5)))
summary(homonymy_first_order_1to5)
summary(homonymy_second_order_1to5)
```

## Homonymy (Gen1-5): Model comparison
```{r}
homonyms_1to5_model.names <- c("Homonymy first order 1 to 5","Homonymy second order 1 to 5")
homonyms_1to5_summ.table <- do.call(rbind, lapply(list(homonymy_first_order_1to5,homonymy_second_order_1to5), broom::glance))
homonyms_1to5_table.cols <- c("df.residual", "deviance", "AIC")
homonyms_1to5_reported.table <- homonyms_1to5_summ.table[homonyms_1to5_table.cols]
names(homonyms_1to5_reported.table) <- c("Resid. Df", "Resid.Dev", "AIC")
homonyms_1to5_reported.table[['dAIC']] <-  with(homonyms_1to5_reported.table, AIC - min(AIC))
homonyms_1to5_reported.table[['AIC_weight']] <- with(homonyms_1to5_reported.table, exp(- 0.5 * dAIC) / sum(exp(- 0.5 * dAIC)))
homonyms_1to5_reported.table$AIC <- NULL
homonyms_1to5_reported.table$AIC_weight <- round(homonyms_1to5_reported.table$AIC_weight, 2)
homonyms_1to5_reported.table$dAIC <- round(homonyms_1to5_reported.table$dAIC, 1)
homonyms_1to5_reported.table$Resid.Dev <- round(homonyms_1to5_reported.table$Resid.Dev, 2)
row.names(homonyms_1to5_reported.table) <- homonyms_1to5_model.names
View(homonyms_1to5_reported.table)
anova(homonymy_first_order_1to5,homonymy_second_order_1to5)
sjPlot::tab_df(homonyms_reported.table,
               file="model comparison homonyms_1to5_.doc")

sjPlot::tab_df(round(coef(summary(homonymy_first_order_1to5)),3),file='homonyms_1to5_fixed_effects.doc')
```


## Homonymy (Gen1-5): Plots of model fit
```{r}
ggplot(df_homonymy[df_homonymy$Generation != 0, ], aes(Generation, Word_repetition, shape=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_first_order_1to5), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy 1to5 by group type - first order model.pdf')

ggplot(df_homonymy[df_homonymy$Generation != 0, ], aes(Generation, Word_repetition, color=GroupType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_second_order_1to5), linetype=GroupType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy 1to5  by group type - second order model.pdf')

ggplot(df_homonymy[df_homonymy$Generation != 0, ], aes(Generation, Word_repetition, shape=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_first_order_1to5), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy")
dev.print(pdf,'Homonymy 1to5 by lexicon type - first order model.pdf')

ggplot(df_homonymy[df_homonymy$Generation != 0, ], aes(Generation, Word_repetition, color=LexiconType)) +
  stat_summary(fun.data=mean_se, geom="pointrange") +
  stat_summary(aes(y=fitted(homonymy_second_order_1to5), linetype=LexiconType),
               fun.y=mean, geom="line") +
  ylab("Proportion of homonymy") 
dev.print(pdf,'Homonymy 1to5  by lexicon type - second order model.pdf')
```

# Consonant repetition (in unique words only)
in progress

```{r}
# uniq <- unique(unlist(data$Date))
# for (i in 1:length(uniq)){
#    data_1 <- subset(data, date == uniq[i])
#    #your desired function
# }
```


